|

### 2021-05-30 appendix/appendix.Rmd
unicameral x non-unicameral binomial tests

In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{Concave means that $b'>0$ and $b''<0$. Convex means that $c'>0$ and $c''>0$. We assume that the derivatives are well defined throughout the analysis. Moreover, we drop the constituency index to make the model more intuitive, so the reader should assume that we always employ a symmetric Nash equilibrium.} The first type of cost, $c_1(x)$, comprises the expenses within the constituency (e. g., hiring a local company for the project). The second type of cost, $c_2(x)$, captures the expenses outside the constituency (e. g., hiring a company from another state). Finally, the third cost, $c_3(x)$, captures the externalities generated by the project (e. g., how much prices shift because local economic factors are being used to provide the project). The total cost is equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$. The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.

@@

```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published) %>%
  rename(`Independent Variables` = indepvar2,
         `Electoral system`      = elecsys2,
         `Estimation method`     = method,
         `Year`                  = year,
         `Published work`        = published)

@@

@@

5. A institution design variable, with:
 - `Unicameral` (e.g., US Municipalities)
 - `Bicameral` (e.g., US States)
 - `Mixed` (e.g., countries with unicameral and bicameral in the same dataset).

@@

```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              sparse = TRUE,
              tdist = TRUE,
              subset = dat$depvar2=='ExpPC',
              slab = dat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = fulldat$depvar2=='ExpPC',
              slab = fulldat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = dat$depvar2=='logExpPC',
              slab = dat$authoryear)

>>>>

In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{For our purposes, concave means that $b'>0$ and $b''<0$. Convex means that $c'>0$ and $c''>0$. We assume that the derivatives are well defined throughout the analysis. Moreover, we drop the constituency index to make the model more intuitive, so the reader should assume that we always employ a symmetric Nash equilibrium.} The first type of cost, $c_1(x)$, comprises the expenses within the constituency (e. g., hiring a local company for the project). The second type of cost, $c_2(x)$, captures the expenses outside the constituency (e. g., hiring a company from another state). Finally, the third cost, $c_3(x)$, captures the externalities generated by the project (e. g., how much prices shift because local economic factors are being used to provide the project). The total cost is equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$. The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.

@@

```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
              year, published, instdesign2) %>%
  rename(`Independent Variables` = indepvar2,
         `Electoral system`      = elecsys2,
         `Estimation method`     = method,
         `Year`                  = year,
         `Published work`        = published,
         `Institution design`    = instdesign2)

@@

We also tested the possibility that the signs change heterogeneously, based on whether the paper studied unicameral versus non-unicameral legislative bodies. This analysis does not take into consideration the size of the upper house, as it would indicate that the cases in the paper had trivially a non-unicameral legislature. The results in the Table XXXX, show that there is no significant change controlling by this variable.

```{r, size="footnotesize", echo = FALSE, cache=TRUE}
aux <- list()
aux[[1]] <- filter(dat, indepvar2 == "N", instdesign2 == 'Unicameral')
aux[[2]] <- filter(dat, indepvar2 == "N", instdesign2 != 'Unicameral')
aux[[3]] <- filter(dat, indepvar2 == "logN", instdesign2 == 'Unicameral')
aux[[4]] <- filter(dat, indepvar2 == "logN", instdesign2 != 'Unicameral')
aux[[1]] <- binom.test(table(aux[[1]]$scoef)[2],
                       sum(table(aux[[1]]$scoef)), p = 0.5)
aux[[2]] <- binom.test(table(aux[[2]]$scoef)[2],
                       sum(table(aux[[2]]$scoef)), p = 0.5)
aux[[3]] <- binom.test(table(aux[[3]]$scoef)[2],
                       sum(table(aux[[3]]$scoef)), p = 0.5)
aux[[4]] <- binom.test(table(aux[[4]]$scoef)[2],
                       sum(table(aux[[4]]$scoef)), p = 0.5)
aux2 <- tidy(aux[[1]])[,-c(2,4,5,6)][,c(3,4,1,2)]
aux2 <- bind_rows(aux2, tidy(aux[[2]])[,-c(2,4,5,6)][,c(3,4,1,2)])
aux2 <- bind_rows(aux2, tidy(aux[[3]])[,-c(2,4,5,6)][,c(3,4,1,2)])
aux2 <- bind_rows(aux2, tidy(aux[[4]])[,-c(2,4,5,6)][,c(3,4,1,2)])
aux2 <- aux2 %>%
  mutate(`Indep. Variable` = c('Lower House Size', 'Lower House Size', 'Log of Lower House Size', 'Log of Lower House Size'),
         `Legislative Inst.` = c('Unicameral', 'Non-unicameral', 'Unicameral', 'Non-unicameral')) %>%
  relocate(`Indep. Variable`, `Legislative Inst.`, .before = method)
aux2$method <- NULL
aux2$alternative <- NULL
pander(aux2)
```

@@

5. A institution design variable, with:
 - `Unicameral` (e.g., US Municipalities)
 - `Non-unicameral`: (e.g. `Bicameral` or `Mixed`).

@@

```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
              sparse = TRUE,
              tdist = TRUE,
              subset = dat$depvar2=='ExpPC',
              slab = dat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = fulldat$depvar2=='ExpPC',
              slab = fulldat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = dat$depvar2=='logExpPC',
              slab = dat$authoryear)
